A new method to estimate dark matter halo concentrations

### 2015-02-23 paper/article.tex
added dv/dx plots
buen acuerdo a altas masas

@@

\begin{equation}
v(<x)=\sqrt{\frac{1}{A}\left[\frac{\ln\left(1+xc\right)}{x}-\frac{c}{xc+1}\right]},
\end{equation}
%
this normalized profile always shows a maximum provided that the
concentration is larger than $c>2$.
It is possible to show that for the NFW profile the maximum is
provided by

@@

Figure \ref{fig:concentration} shows the mass-concentration
relationship from the N-body data with the results of the three
different methods.
The central lines correspond the median and the
shadowed region indicates the quartiles.
In this relationship our methods represents a compromise between the
velocity and density methods.
The slope is flatter and the overall normalization is below the
velocity method and above the density.

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.48\textwidth]{dv_dx.pdf}
  \includegraphics[width=0.48\textwidth]{zeros.pdf}
\end{center}
\caption{Dimensionless derivative of the velocity profile as a
  function of the dimensionless radius for different concentration
  values. \label{fig:profiles}}
\end{figure*}

@@

\begin{equation}
v(<x)=\sqrt{\frac{1}{A}\left[\frac{\ln\left(1+xc\right)}{x}-\frac{c}{xc+1}\right]},
\end{equation}

\begin{equation}
\frac{dv}{dx}=\frac{1}{A}\frac{\frac{2cx+1}{\left(cx+1\right)^{2}}cx-\log\left(cx+1\right)}{2x^{2}v\left(x\right)}
\end{equation}
%
this normalized profile always shows a maximum provided that the
concentration is larger than $c>2$.
It is possible to show that for the NFW profile the maximum is
provided by

@@

Figure \ref{fig:concentration} shows the mass-concentration
relationship from the N-body data with the results of the three
different methods.
The central lines correspond the median and the
shadowed region indicates the quartiles.
In this relationship our methods represents a compromise between the
velocity and density methods.
The slope is flatter and the overall normalization is below the
velocity method and above the density.
We also note that at high masses ($M>10^{14}\hMsun$) our method 
and the velocity method show a reasonable agreement within the
uncertainties.
